---
title: "Overview of Linear Models"
output: pdf_document
---

\renewcommand{\vec}[1]{\mathbf{#1}}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height = 4, fig.width = 6, fig.align = 'center')
library(tidyverse) 
library(rstanarm)
library(arm)
library(gridExtra)
set.seed(11012020)
```

### Building and comparing regression models for prediction

\vfill

1. Include all input variables that, for substantive reasons, might be expected to be important in predicting the outcome.

\vfill

2. It is not always necessary to include these inputs as separate predictors 

\vfill

3. For inputs that have large effects, consider including their interactions as well.

\vfill

4. Use standard errors to get a sense of uncertainties in parameter estimates. Know these will change if new predictors are added to the model.

\vfill

5. Make decisions about including or excluding predictors based on a combination of contextual understanding (prior knowledge), data, and the uses of the regression model
    a. If the coefficient of a predictor is estimated precisely, generally makes sense to keep it in the model
\vfill
    b. If the standard error is large and there seems to be no substantive reason to include it in the model, it can make sense to remove it.
\vfill  
    c. If the predictor is important for the problem at hand (groups interested in comparing or controlling for), generally recommend keeping it in the model.
\vfill  
    d. If a coefficient does not make sense (unexpected sign), try to understand how this could happen.
  
\vfill



\newpage

###  10 tips to improve your regression modeling

From appendix B

1. Think about variation and replication
\vfill

2. Forget about statistical significance
\vfill

3. Graph the relevant and not the irrelevant

    a. Graph the fitted model
    b. Make many graphs
    c. Don't graph the irrelevant
\vfill

4. Interpret regression coefficients as comparisons

\vfill

5. Understand statistical methods using fake-data simulations

\vfill

6. Fit many models

\vfill

7. Set up a computational workflow

    a. Data subsetting
    b. Fake-data and predictive simulation
  
\vfill

8. Use transformations

\vfill

9. Do causal inference in a targeted way

\vfill

10. Learn methods through live examples.

\newpage


### Assumptions for Regression Models

```{r, echo = F, message = F}
beer <- read_csv('http://math.montana.edu/ahoegh/Data/Brazil_cerveja.csv')
```

The assumptions described in _Regression and Other Stories,_ are more broad than many textbooks. In order of importance,

\vfill


\vfill

\vfill

\vfill

\vfill

\vfill

\vfill

\newpage


### Regression with Multiple Predictors

More beer...

```{r, echo = F, message = F}
beer <- read_csv('http://math.montana.edu/ahoegh/Data/Brazil_cerveja.csv')
```


Now consider jointly considering both weekend/weekday and maximum temperature. The model can now be written as

$$y = \beta_0 + \beta_1 x_{weekend = 1} + \beta_2 x_{tmp} + \epsilon,$$
where:

- $y$ is the beer consumption, 
\vfill

- $\beta_0$ 

\vfill

- $\beta_1$ 

\vfill

- $\beta_2$ 

\vfill

```{r}
ml_regression <- beer %>% stan_glm(consumed ~ weekend + max_tmp, data = ., refresh = 0)
ml_regression
```

\newpage

#### Coefficient Interpretation

- When interpreting coefficients in a multiple regression model, it is important to understand that these values control for other predictors in the model!

\vfill

The textbook puts an emphasis on differentiating predictive and counterfactual interpretations:

- The predictive interpretation focuses on how the outcome differs, on average, when _comparing_ two groups of items that differ by 1 unit (and all other predictors are the same). 

\vfill
- The counterfactual interpretation focuses on how the outcome would differ with an individual, rather than between individuals. 

\vfill

The counterfactual interpretation should be reserved for a situation where causal inferences are reasonable, such as a completely randomized experimental design.

\vfill

It is easy to get careless with wording and say things like "a change in temperature is associated with a change in consumption," but 

\vfill
